---
title: "CO2_2022-08-29"
author: "Kayla Emerson"
date: '2022-09-12'
output: html_document
---

### download relevant libraries 
```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(plotly)
library(here)

knitr::opts_chunk$set(echo = TRUE)
```

##About
This file processes CO2 data for the Currituck and Croatan Sounds Wetland Project

### We start by reading in and then cleaning data
```{r setup, include=FALSE}

#enter date of sampling to be processed, locate it in working directory 
folder <- "2022-08-29"
setwd(here::here(paste("CO2/"), folder))

#pulls out csv files from folder 
all_files=list.files(pattern=".csv") 

#create site names by removing underscores from files

sites_rp = sapply(strsplit(all_files, "_"), function(x) x[2])
site_names=unique(sites_rp) #creates list of site names for following loop


#rm old files, if they exist
rm(CO2Data)
rm(Temp_CO2Data)

for (site in site_names){
 # if(str_contains("CO2"){
  list1=list.files(pattern=site) #finds all files for the site
  sitelist_csv=grep(".csv",list1) #creates list of all files for site
  file_list=list1[sitelist_csv]
  
  #reads in files in list and appends
  for (file in file_list){
    if (!exists("CO2Data")){
      CO2Data <- read.csv(file, skip=6, header = TRUE)
      CO2Data=CO2Data[,1:3]
        if(names(CO2Data)[1] == "Date"){
          colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
      } else { 
        colnames(CO2Data) <- c("Date","Time","ppm")
        CO2Data$DateTime <- as.POSIXct(paste(CO2Data$Date, CO2Data$Time), format="%d/%m/%Y %H:%M:%S", tz = "UTC")
      }
      
      CO2Data$Station <- site
    }
    if (exists("CO2Data")) {
      Temp_CO2Data <- read.csv(file, skip=6, header = TRUE)  
      Temp_CO2Data=Temp_CO2Data[,1:3]
      if(colnames(Temp_CO2Data)[1]=="Date"){
        colnames(Temp_CO2Data) <- c("Date","Time","ppm")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Date, Temp_CO2Data$Time), format="%m/%d/%Y %I:%M:%S %p", tz = "UTC")
        Temp_CO2Data$Station <- site
      } else {
#        Temp_CO2Data$Fecha <- as.Date(Temp_CO2Data$Fecha, format = "%d / %m / %Y")
        Temp_CO2Data$DateTime <- as.POSIXct(paste(Temp_CO2Data$Fecha, Temp_CO2Data$Tiempo), format="%d/%m/%Y%H:%M:%S", tz = "UTC")
        colnames(Temp_CO2Data) <- c("Date","Time","ppm","DateTime")
        Temp_CO2Data$Station <- site
      }
      CO2Data <- rbind(CO2Data, Temp_CO2Data)
      rm(Temp_CO2Data)
    }
    
  }
  
 #  CO2Data$DateTime <- round_date(CO2Data$DateTime, "15 mins") #Round if needed
  CO2Data=unique(CO2Data)
  CO2Data$Date <- NULL
  CO2Data$Time <- NULL
   CO2Data$ppm <- as.numeric(as.character(CO2Data$ppm))
  CO2Data <- CO2Data[,c(3,2,1)]
  assign((paste(site,sep="_")),CO2Data) #creates object with new appended data
  rm(CO2Data) #removes CO2 data so that multiple sites aren't appended together
}


```

## Clean up CO2 data 
select data for each desired times
```{r pressure, echo=FALSE}

```


## Correct viasalas temperature and pressure with HOBO data for the time period we collected data
** WORK IN PROGRESS- NEED WL DATA **
Used a new vaisla labeled box 1

```{r pressure, echo=FALSE}

folder <- "2022-08-29"
setwd(here::here(paste("CO2/"), folder))


# first, read in WL hobo at -10m
waterlevel_n10 <- read.csv(here::here(paste("Injections/"), folder ,"/Injection_Temp_xn10_2022-07-01.csv"),skip=1)
waterlevel_n10 <- waterlevel_n10[,c(2:4)]
colnames(waterlevel_n10) <- c("DateTime", "WL_Pressure", "Temp")

# format DateTime in WL 
waterlevel_n10$DateTime <- as.POSIXct(paste(waterlevel_n10$Date, waterlevel_n10$Time), format="%m/%d/%y %I:%M:%S %p", tz = "UTC")
# correct kpa to hpa 
##1 kPa = 10 hPa
##1 kPa = 0.101972 m
waterlevel_n10$WL_Pressure <- waterlevel_n10$WL_Pressure * 10
#full_join to join CO2 data to WL by datetime
df_corr <- full_join(df_new, waterlevel_n10, by = "DateTime" )
# clean data <- remove NA values bc vaisala reads every 1s and WL reads ever 10s
df_corr <- na.omit(df_corr) 


```

## Correct new Vaisalas
** WORK IN PROGRESS. NEED WL DATA **
New vaisalas need to be corrected for just pressure

```{r check CO2 data plot, echo=FALSE}

# Now correct the adjusted ppm 
df_corr$adjusted_ppm <- (df_newv$ppm  )* (1 + (1013 - df_newv$WL_Pressure) * 0.0015)

# Now correct for individual vaisala calibration

#Box 1 New
df_newv <- df_newv %>% 
df_newv$adjusted_ppm <- (df_newv$adjusted_ppm * 1.00054) + 65.15813

```

## Plot CO2 for Well 1

```{r check CO2 data plot, echo=FALSE}

well1 <- filter(PIS1, DateTime >= as.POSIXct("2022-08-29 13:16:00", tz = "UTC") & DateTime < as.POSIXct("2022-08-29 13:36:00", tz = "UTC"))

##check data
plot_ly(well1,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```

## Plot CO2 for Surface 1

```{r check CO2 data plot, echo=FALSE}
##check data
surf1 <- filter(PIS1, DateTime >= as.POSIXct("2022-08-29 13:44:00", tz = "UTC") & DateTime < as.POSIXct("2022-08-29 14:04:00", tz = "UTC"))

##check data
plot_ly(surf1,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```

## Plot CO2 for Well 2

```{r check CO2 data plot, echo=FALSE}
##check data
well2 <- filter(PIS2, DateTime >= as.POSIXct("2022-08-29 16:02:00", tz = "UTC") & DateTime < as.POSIXct("2022-08-29 16:53:00", tz = "UTC"))

##check data
plot_ly(well2,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```

## Plot CO2 for Surface 2

```{r check CO2 data plot, echo=FALSE}
##check data
surf2 <- filter(PIS2, DateTime >= as.POSIXct("2022-08-29 17:04:00", tz = "UTC") & DateTime < as.POSIXct("2022-08-29 17:25:00", tz = "UTC"))

##check data
plot_ly(surf2,
    x = ~DateTime, y = ~ppm, type = 'scatter', mode = 'markers') 
```